### 2013-07-10 tests_Mg.Rmd
extra results

source("gapolyfuncs.R")
report <- make.report(my.data, population=250, iterations=50)

@@

write.table(df, "Mg250.txt")
# df <- read.table("Mg250.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Mg dataset")

########################################################
# Lambda Test
lambda.values <- seq(0.5,0.999,length.out=20)
n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=50, iterations=25)

df <- data.frame(error = as.vector(matrix(errors,nrow=1)),
                 lambda = as.factor(rep(round(lambda.values,3), each=n.runs)))

@@

df <- read.table("lambda.errors.Mg.txt", header=TRUE)

df$lambda <- as.factor(df$lambda)

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Mg250 dataset")
##############################################
# Check fitness progress

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=250, iterations=50, lambda=0.975)

@@

write.table(df, "Mg250_lamda0.975.txt")
# df <- read.table("Mg250.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Mg dataset (lambda 0.975)")

########################################################
# Lambda Test
lambda.values <- seq(0.5,1.5,length.out=20)
n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=50, iterations=50)

df <- data.frame(error = as.vector(matrix(errors,nrow=1)),
                 lambda = as.factor(rep(round(lambda.values,2), each=n.runs)))

@@

df <- read.table("lambda.errors.Mg.txt", header=TRUE)
df$lambda <- as.factor(df$lambda)

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Mg dataset")
##############################################
# Check fitness progress
